%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    {\Huge \scshape Abhijay Rajvansh} \\ \vspace{1pt}
    Software Engineer, AI Agents and SaaS Developer! \\ \vspace{1pt}

    \small\href{mailto:abhijayrajvansh.work@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{abhijayrajvansh.work@gmail.com}} ~
    \href{https://www.linkedin.com/in/abhijayrajvansh/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin/abhijayrajvansh}}  ~
    \href{https://github.com/abhijayrajvansh}{\raisebox{-0.2\height}\faGithub\ \underline{github/abhijayrajvansh}} ~
    \href{www.abhijayrajvansh.com}{\raisebox{-0.2\height}\  \underline{visit my portfolio}} ~
    \vspace{-8pt}
\end{center}



%-----------Technical Skills-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Applied AI \& Infra}{: \textbf{LLMs}, \textbf{RAG Pipelines}, Multi-Agent Systems, \textbf{LangChain}, \textbf{LangGraph}, LlamaIndex, \textbf{n8n}, MCP (Model Context Protocol), A2A (Agent-to-Agent Protocol), Hugging Face, Ollama, Guardrails, Structured Outputs, \textbf{Tool-Calling}, \textbf{vLLM}, Ray Serve, KServe, TGI, \textbf{Open-Source LLMs (Qwen, Kimi, FLUX)}, \textbf{GGUF}, Continuous Batching, Speculative Decoding, Prefix Caching, \textbf{Quantization (FP8/INT8/INT4)}, LoRA/QLoRA Fine-Tuning, safetensors, OpenAI-Compatible APIs, \textbf{YOLO}, OpenCV, TensorFlow} \\
   \textbf{Languages \& Frameworks}{: TypeScript (JavaScript), Python, C++, Bash, Go, Next.js, Node.js, Express.js, React, Django, FastAPI, Pandas, NumPy, Prisma ORM} \\
   \textbf{Databases}{: \textbf{Vector DBs}: \textbf{Pinecone}, \textbf{Weaviate}, \textbf{Milvus}, Chroma; \textbf{SQL}: \textbf{PostgreSQL}, \textbf{MySQL}, MSSQL, Oracle DB, SQLite, ClickHouse, CockroachDB, BigQuery; \textbf{NoSQL}: \textbf{MongoDB}, \textbf{Redis}, Cassandra, DynamoDB, Elasticsearch, Supabase, Firebase Realtime DB, Firestore} \\
   \textbf{Data Science}{: Apache Superset, Power BI, Tableau, Metabase, Grafana, dbt, Jupyter Notebooks, SSIS, SQL Server Agent, SSISDB, SSDT, OLE DB, ADO.NET, ODBC, Incremental Loads, Change Data Capture, Data Warehousing} \\
   \textbf{DevOps \& Cloud}{: Git, Linux, CI/CD, GitHub Actions, Docker, Kubernetes, Nginx, Cloudflare, AWS, GCP, Azure} \\
  }}
 \end{itemize}
 \vspace{-16pt}


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Brackets}{Oct 2025 -- Present}
      {Member of Technical Staff}{Gurugram, Haryana, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented LLM-driven AI agents in close collaboration with product teams, reducing human input in operational processes by 95\%.}
        \resumeItem{Authored a white paper defining an Open Banking System Design for API developers, covering layered architecture and end-to-end business workflow strategies.}
        \resumeItem{Led technical discussions with stakeholders to translate business requirements into functional AI features, maintaining alignment across timelines and delivery goals.}
        \resumeItem{Introduced agile delivery practices within the engineering team, improving responsiveness to changing requirements and overall project throughput.}
      \resumeItemListEnd

    \resumeSubheading
      {Uptut}{Sept 2024 -- Present}
      {Technical Trainer \& Consultant}{Gurugram, Haryana, India}
      \resumeItemListStart
        \resumeItem{Deliver training programs in AI fundamentals, Agentic AI, and LLM-based workflow automation for enterprise engineering teams.}
        \resumeItem{Train cohorts on relational and NoSQL databases including MySQL, PostgreSQL, MSSQL, Oracle, and MongoDB, covering schema design, query optimization, indexing, and production deployment.}
        \resumeItem{Conduct full-stack development programs covering React, Next.js, Node.js, REST/GraphQL APIs, and end-to-end deployment pipelines.}
        \resumeItem{Run hands-on AI computer vision workshops applying YOLO, CNNs, and OpenCV for real-world detection and classification use cases.}
        \resumeItem{Support clients on analytics stack setup and dashboard reporting using Apache Superset and Power BI.}
        \resumeItem{Deliver ETL and data pipeline training covering SSIS, SQL Server Integration Services, incremental load patterns, error handling, package deployment to SSISDB, and scheduling via SQL Server Agent for enterprise data and BI teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Bling Cloud, Techstars'23}{Feb 2023 -- November 2023}
      {Software Engineer (Founding Team)}{Remote, San Francisco Bay Area}
      \resumeItemListStart
        \resumeItem{Engineered the MVP for an innovative cloud platform, integrating with major messaging services to facilitate seamless user interaction.}
        \resumeItem{Designed and implemented secure APIs for user authentication and profile management, enhancing user experience and platform reliability.}
        \resumeItem{Provided mentorship to interns, fostering growth, and optimizing development practices to maintain code quality and performance levels.}
        \resumeItem{Committed to remote collaboration across time zones, adapting to US standards for timely product updates and deployments.}
      \resumeItemListEnd

    \resumeSubheading
      {Apple, iMac Labs, SRMIST}{Oct 2022 -- November 2022}
      {Software Engineer, iOS Design}{Chennai, TN}
      \resumeItemListStart
        \resumeItem{Selected from a competitive pool of 18,000 candidates for prestigious iOS App Development program, highlighting exceptional skill and potential.}
        \resumeItem{Developed a functional prototype app through rigorous testing and debugging, achieving a seamless user experience.}
        \resumeItem{Demonstrated superior problem solving by addressing and resolving runtime errors, enabling the project's advancement to the next development stage.}
      \resumeItemListEnd

    \resumeSubheading
      {NHS UK}{Jul 2022 -- October 2022}
      {AI Research Intern, Object Detection}{Remote, Luton, England, United Kingdom}
      \resumeItemListStart
        \resumeItem{Directed a critical project that applied deep learning techniques to automate orthopedic implant identification, achieving a predictive accuracy of 97\%.}
        \resumeItem{Utilized advanced algorithms, including YOLOv7 and CNN, to enhance model performance and reliability in medical applications.}
        \resumeItem{Collaborated with medical professionals to ensure alignment of technical solutions with clinical requirements and standards.}
      \resumeItemListEnd

    \resumeSubheading
      {Unacademy}{Mar 2022 -- October 2022}
      {Algorithms Educator \& TA}{Delhi, India}
      \resumeItemListStart
        \resumeItem{Instructed students on key programming concepts including Data Structures and OOP, effectively boosting understanding through personalized support.}
        \resumeItem{Resolved over 500 coding queries, utilizing strategic problem-solving to suggest optimized solutions and enhance learning outcomes.}
        \resumeItem{Facilitated virtual learning sessions, adapting educational strategies to engage diverse student backgrounds and enhance comprehension.}
      \resumeItemListEnd

    \resumeSubheading
      {IEEE}{Nov 2021 -- September 2022}
      {Research And Development Engineer}{Chennai, Tamil Nadu, India}
      \resumeItemListStart
        \resumeItem{Collaborated in interdisciplinary teams on AI/ML projects tailored for the healthcare and engineering sectors, optimizing project outcomes.}
        \resumeItem{Documented research findings and technical specifications to support innovative solutions in AI applications across various domains.}
        \resumeItem{Contributed to the development of streamlined processes that improved project timelines and deliverables through efficient teamwork.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Publications and Research}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Open Banking System Design \& Architecture} $|$ \emph{White Paper}}{November 2024}
          \resumeItemListStart
            \resumeItem{Authored a comprehensive framework analyzing Open Banking implementations across UK, EU, India, and Africa, impacting 50+ financial institutions.}
            \resumeItem{Developed a layered architectural model achieving 99.9\% uptime for API services while reducing integration time by 60\%.}
            \resumeItem{Introduced standardized protocols resulting in 40\% cost reduction in Banking-as-a-Service (BaaS) implementations.}
            \resumeItem{Established security and data governance frameworks adopted by 15+ banking partners, protecting over 1M+ customer transactions.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Object Detection for Orthopaedic Implants} $|$ \emph{Research Paper}}{July 2022}
          \resumeItemListStart
            \resumeItem{Developed an AI-powered detection system for Total Hip Arthroplasty implants, achieving 97\% accuracy in identification.}
            \resumeItem{Reduced preoperative planning time by 75\% through automated implant analysis, benefiting 1000+ surgical cases annually.}
            \resumeItem{Implemented deep learning algorithms resulting in 90\% reduction in manual identification errors and 65\% cost savings.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------OPEN SOURCE-----------
\section{Open Source Contributions}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI Frameworks \& Fullstack SDK} $|$ \emph{TypeScript, Python, LLMs}}{2024 -- Present}
          \resumeItemListStart
            \resumeItem{Developed high-performance chat inference system with Ollama LLMs, achieving 40\% faster response times.}
            \resumeItem{Created comprehensive SDK for AI applications, serving 2000+ monthly developers.}
            \resumeItem{Implemented efficient vector storage solutions, reducing embedding costs by 35\% while maintaining accuracy.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Solana Labs \& ZetaChain} $|$ \emph{Rust, Blockchain}}{2024}
          \resumeItemListStart
            \resumeItem{Contributed to Solana's core protocol improvements and smart contract optimizations, impacting 1M+ daily transactions.}
            \resumeItem{Enhanced ZetaChain protocol contracts, implementing cross-chain functionality used by 50k+ users.}
            \resumeItem{Developed security patches and performance improvements, reducing transaction validation time by 25\%.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Trading Bots, Crypto Wallet Generator \& NextUI} $|$ \emph{TypeScript, React}}{2022}
          \resumeItemListStart
            \resumeItem{Built open-source crypto wallet trading bot tool with supporting centralized exchange like Binance and CoinDCX.}
            \resumeItem{Contributed UI components to NextUI library, improving accessibility and mobile responsiveness for 10k+ developers.}
            \resumeItem{Authored comprehensive documentation and integration guides, reducing implementation time by 60\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------INVOLVEMENT---------------
\section{Awards and Achievements}
    \begin{itemize}[itemsep=-5pt, parsep=3pt]
        \item Winner at Smart India Hackathon 2023 (Healthcare Project).
        \item Qualified for Facebook/Meta Hacker Cup 2022 Round 1, secured Global Rank 6994.
        \item Google Hash Code 2022 - Global Rank 4895, Country Rank 804 among 10,000+ participating teams.
        \item Secured University Rank 2 in Coding Ninjas Intra-College Competition'2021 among 8,000+ participants.
        \item National Cyber Olympiad (NCO 2018) - Achieved State Rank 1 and All India Rank 16.
    \end{itemize}
\vspace*{2.0\multicolsep}
%\resumeSubHeadingListEnd

% ------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item Data Structures
                \item Software Methodology
                \item Algorithms Analysis
                \item Database Management
                \item Artificial Intelligence
                \item Internet Technology
                \item Systems Programming
                \item Computer Architecture
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

% -----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Self Taught: AI, LLMs and Full-Stack Development}{Sep. 2024 -- Present}
    {Learning and Building}{Remote}
  \resumeSubheading
    {Harvard's CS50: Introduction to Computer Science}{Sep. 2023 -- May 2024}
    {Online Course}{edX Platform}
  \resumeSubheading
    {SRM Institute of Science and Technology}{Sep. 2020 -- Dec 2023}
    {Completed coursework with 3.9 GPA towards a Bachelor's in Computer Science}{Chennai, TN}
\resumeSubHeadingListEnd


\end{document}
